---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cengenDataSC



Data from the CeNGEN project as R objects.


## Installation

Install from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AlexWeinreb/cengenDataSC")
```
## Example

Use `data()` to load the dataset of interest:

```{r}
data("cengen_sc_2", package = "cengenDataSC")

dim(cengen_sc_2)
```

You can use the binarized matrix to mask the TPM matrix, and obtain the tables as available on the website:

```{r}
data("cengen_TPM", package = "cengenDataSC")

cengen_TPM <- cengen_TPM[rownames(cengen_sc_2), - which(endsWith(colnames(cengen_TPM), "stressed"))]

(cengen_sc_2 * cengen_TPM)[1005:1010,1:5]

```

## Additional informations and citation

Information on the website: https://cengen.org

See the preprint describing the data: [Taylor *et al.*, Molecular topography of an entire nervous system](https://www.biorxiv.org/content/10.1101/2020.12.15.422897v2).

